---
title: "Towards Personalized Decisions for Prostate Cancer Biopsies in Active Surveillance"
author: "Anirudh Tomer and Dimitris Rizopoulos"
date: "`r Sys.Date()`"
output:
  ioslides_presentation:
    css: main.css
    widescreen: yes
    mathjax: default
    logo: emc.png
transition: none
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library("ggplot2")
library("ggpubr")
library("shiny")
library("shinyBS")
library("lattice")
library("JM")

load("plotJM_data.RData")
load("presentationData.Rdata")
load("PRIAS.RData")
scheduleResCombined$methodName <- factor(scheduleResCombined$methodName,
                                         levels = levels(scheduleResCombined$methodName),
                                         labels = c("Annual", "PRIAS", "15%", 
                                                    "5%", "F1"))

FONT_SIZE = 15
POINT_SIZE = 3
LARGE_POINT_SIZE = 6
# 
# pat_1757$log2psaplus1 = log(pat_1757$psa + 1, base = 2)
# pat_1757$high_dre = ifelse(pat_1757$dre=="T1c", 0, 1)


plot_delay =  ggplot() + 
  geom_point(aes(x=c(0, 4, 7), y=0, shape="A", color="A"), size=LARGE_POINT_SIZE) + geom_point(aes(x=5.5, y=0, shape="B", color="B"), size=LARGE_POINT_SIZE) + 
  geom_ribbon(aes(x=c(5.5, 7), ymin=0,ymax=Inf), alpha=0.2) +
  geom_label(aes(x=6.25, y=0.1, label="Delay"), size=5) +
  xlab("Follow-up time (years)") + ylab("") + ylim(0, 0.2) +
  scale_shape_manual("", 
                     labels=c("Biopsies", "Time of cancer progression (unobserved)"),
                     values=c(18,15)) + 
  scale_color_manual("", 
                     labels=c("Biopsies", "Time of cancer progression (unobserved)"),
                     values=c("black", "red3")) + 
  scale_x_continuous(breaks=c(0,4,5.5,7)) + 
  theme(text=element_text(size=FONT_SIZE), axis.line.y = element_blank(), axis.ticks.y = element_blank(), axis.text.y = element_blank(), plot.margin = margin(0,0,0,0),
        legend.position = "bottom", legend.direction = "horizontal", axis.line.x = element_line())

plot_annual_delay =  ggplot() + 
  geom_point(aes(x=c(0:6), y=0, shape="A", color="A"), size=LARGE_POINT_SIZE) + geom_point(aes(x=5.5, y=0, shape="B", color="B"), size=LARGE_POINT_SIZE) + 
  geom_ribbon(aes(x=c(5.5, 6), ymin=0,ymax=Inf), alpha=0.2) +
  geom_label(aes(x=5.75, y=0.1, label="Delay"), size=5) +
  xlab("Follow-up time (years)") + ylab("") + ylim(0, 0.2) +
  scale_shape_manual("", 
                     labels=c("Biopsies", "Time of cancer progression (unobserved)"),
                     values=c(18,15)) + 
  scale_color_manual("", 
                     labels=c("Biopsies", "Time of cancer progression (unobserved)"),
                     values=c("black", "red3")) + 
  scale_x_continuous(breaks=c(0:6, 5.5)) + 
  theme(text=element_text(size=FONT_SIZE), axis.line.y = element_blank(), axis.ticks.y = element_blank(), axis.text.y = element_blank(), plot.margin = margin(0,0,0,0),
        legend.position = "bottom", legend.direction = "horizontal", axis.line.x = element_line())

plot_prias_delay = ggplot() + 
  geom_point(aes(x=c(0, 4, 6), y=-20, shape="A", color="A"), size=LARGE_POINT_SIZE) + 
    geom_point(aes(x=5.5, y=-20, shape="B", color="B"), size=LARGE_POINT_SIZE) + 
    geom_line(aes(x=c(0,0.25,0.5,0.75,1, 1.25,1.5,1.75,2,2.5,3,3.5,4,4.5,5,5.5,6),y=c(-5,-8, -4,15,19, 20,21,18,33,12,11,14,16,17,28,3,7)), alpha=0.2) +
    geom_point(aes(x=c(0,0.25,0.5,0.75,1, 1.25,1.5,1.75,2,2.5,3,3.5,4,4.5,5,5.5,6),y=c(-5,-8, -4,15,19, 20,21,18,33,12,11,14,16,17,28,3,7), shape="C", color="C"), size=POINT_SIZE) +
  geom_ribbon(aes(x=c(5.5, 6), ymin=-20,ymax=-10), alpha=0.2) +
    geom_ribbon(aes(x=c(0, 6), ymin=0,ymax=10), alpha=0.2, fill="red3") +
  geom_label(aes(x=5.75, y=-15, label="Delay"), size=5) +
    geom_label(aes(x=3, y=5, label="Annual biopsy when PSA-DT is in this region"), size=5) +
  xlab("Follow-up time (years)") + ylab("PSA doubling time")+
  scale_shape_manual("", 
                     labels=c("Biopsies", "Time of cancer progression (unobserved)", "PSA-DT"),
                     values=c(18,15,16)) + 
  scale_color_manual("", 
                     labels=c("Biopsies", "Time of cancer progression (unobserved)", "PSA-DT"),
                     values=c("black", "red3", "dodgerblue4")) + 
  scale_x_continuous(breaks=c(0,4,5.5,6)) + 
    scale_y_continuous(breaks=seq(-10,40, by=10))+
  theme(text=element_text(size=FONT_SIZE), plot.margin = margin(0,0,0,0),
        legend.position = "bottom", legend.direction = "horizontal", axis.line.x = element_line(), axis.line.y.left = element_line())

plot_obs_psa_data = ggplot() + 
    geom_line(data=pat_1757[!is.na(pat_1757$psa),], aes(x=visitTimeYears, y=psa), alpha=0.2, color="dodgerblue4") +
    geom_point(data=pat_1757[!is.na(pat_1757$psa),], aes(x=visitTimeYears, y=psa), shape=16, size=POINT_SIZE, color="dodgerblue4") + 
    geom_vline(data=pat_1757[!is.na(pat_1757$gleason),], aes(xintercept=visitTimeYears, linetype="Biopsies"), size=0.7) +
    scale_linetype_manual("", values="dotted", label="Biopsies") +
  theme(text=element_text(size=FONT_SIZE), plot.margin = margin(0,r = 20,0,0),
        legend.position = "bottom", legend.direction = "horizontal", axis.line.y.left = element_line(), axis.line.x = element_line()) + 
  xlab("Follow-up time (years)") + ylab("PSA (ng/mL)") 

plot_obs_dre_data = ggplot() + 
    geom_line(data=pat_1757[!is.na(pat_1757$high_dre),], aes(x=visitTimeYears, y=high_dre), alpha=0.2, color="darkorchid") +
    geom_point(data=pat_1757[!is.na(pat_1757$high_dre),], aes(x=visitTimeYears, y=high_dre), shape=17, size=POINT_SIZE, color="darkorchid") + 
    geom_vline(data=pat_1757[!is.na(pat_1757$gleason),], aes(xintercept=visitTimeYears, linetype="Biopsies"), size=0.7) +
    scale_linetype_manual("", values="dotted", label="Biopsies") +
  scale_y_continuous(breaks=0:1, labels=c("T1c", "above T1c"), limits = c(0,1)) + 
  theme(text=element_text(size=FONT_SIZE), plot.margin = margin(0,0,0,l=20),
        legend.position = "bottom", legend.direction = "horizontal", axis.line.y.left = element_line(), axis.line.x = element_line()) + 
  xlab("Follow-up time (years)") + ylab("DRE (binary)")
  
plot_obs_data = ggarrange(plot_obs_psa_data, plot_obs_dre_data, nrow=1, ncol=2,
                                  common.legend = T, legend = "bottom")

plot_sim_study_progtime = ggplot() + geom_histogram(aes(x=sim_study_prog_time[sim_study_prog_time!=10]), bins=20) + xlab("Cancer progression time (years)") + ylab("Count") + theme(text=element_text(size=FONT_SIZE), plot.margin = margin(0,0,0,0), axis.line.x = element_line(), axis.line.y.left = element_line())

# Joint model association parameters
plot_jmFitAssocParam = ggplot(data=jointFitAssocRes) + geom_errorbar(aes(x=assoc, ymin=lower, ymax=upper), width=0.1) + geom_point(aes(x=assoc, y=mean), size=POINT_SIZE) +
  xlab("") + ylab(expression("log Hazard Ratio (95% CI)")) + 
  theme(text = element_text(size=FONT_SIZE),  legend.position = "none")

#All patients boxplot
boxplot_nb_all = ggplot() + geom_boxplot(data = scheduleResCombined, aes(x=methodName, y=nb, color=type), outlier.shape = NA) + scale_y_continuous(breaks=c(1,4,7,10)) + theme(text=element_text(size=FONT_SIZE), legend.title = element_blank(), axis.line = element_line()) + xlab("Method") + ylab("Number of biopsies") + coord_flip() + geom_hline(yintercept = 3, linetype='dashed', color='black')

boxplot_offset_all =  ggplot() + geom_boxplot(data = scheduleResCombined[scheduleResCombined$progression_time<10,], aes(x=methodName, y=offset, color=type), outlier.shape = NA)  + theme(text=element_text(size=FONT_SIZE), legend.title = element_blank(), axis.line = element_line(), axis.title.y = element_blank()) + xlab("Method") + ylab("Delay in detection\n of cancer progression (years)") + coord_flip(ylim = c(0,5)) + geom_hline(yintercept = 2, linetype='dashed', color='black')

boxplot_all = ggarrange(boxplot_nb_all, boxplot_offset_all, common.legend = T, align = "h", legend = "bottom")

#Fast patients boxplot
boxplot_nb_fast = ggplot() + geom_boxplot(data = scheduleResCombined[scheduleResCombined$progression_time>0 & scheduleResCombined$progression_time<=3.5,], aes(x=methodName, y=nb, color=type), outlier.shape = NA)  + theme(text=element_text(size=FONT_SIZE), legend.title = element_blank(), axis.line = element_line()) + xlab("Method") + ylab("Number of biopsies") + coord_flip() + geom_hline(yintercept = 3, linetype='dashed', color='black')

boxplot_offset_fast =  ggplot() + geom_boxplot(data = scheduleResCombined[scheduleResCombined$progression_time>0 & scheduleResCombined$progression_time<=3.5,], aes(x=methodName, y=offset, color=type), outlier.shape = NA)  + theme(text=element_text(size=FONT_SIZE), legend.title = element_blank(), axis.line = element_line(), axis.title.y = element_blank()) + xlab("Method") + ylab("Delay in detection\n of cancer progression (years)") + coord_flip(ylim = c(0,4.5)) + geom_hline(yintercept = 2, linetype='dashed', color='black')

boxplot_fast = ggarrange(boxplot_nb_fast, boxplot_offset_fast, common.legend = T, align = "h", legend = "bottom")

#Intermediate patients boxplot
boxplot_nb_intermediate = ggplot() + geom_boxplot(data = scheduleResCombined[scheduleResCombined$progression_time>3.5 & scheduleResCombined$progression_time<10,], aes(x=methodName, y=nb, color=type), outlier.shape = NA)  + theme(text=element_text(size=FONT_SIZE), legend.title = element_blank(), axis.line = element_line()) + xlab("Method") + ylab("Number of biopsies") + coord_flip() + geom_hline(yintercept = 3, linetype='dashed', color='black')

boxplot_offset_intermediate =  ggplot() + geom_boxplot(data = scheduleResCombined[scheduleResCombined$progression_time>3.5 & scheduleResCombined$progression_time<10,], aes(x=methodName, y=offset, color=type), outlier.shape = NA)  + theme(text=element_text(size=FONT_SIZE), legend.title = element_blank(), axis.line = element_line(), axis.title.y = element_blank()) + xlab("Method") + ylab("Delay in detection\n of cancer progression (years)") + coord_flip(ylim = c(0,6)) + geom_hline(yintercept = 2, linetype='dashed', color='black')

boxplot_intermediate = ggarrange(boxplot_nb_intermediate, boxplot_offset_intermediate, common.legend = T, align = "h", legend = "bottom")

#Slow patients boxplot
boxplot_nb_slow = ggplot() + geom_boxplot(data = scheduleResCombined[scheduleResCombined$progression_time==10,], aes(x=methodName, y=nb, color=type), outlier.shape = NA) + scale_y_continuous(breaks=c(1,4,7,10)) + theme(text=element_text(size=FONT_SIZE), legend.title = element_blank(), axis.line = element_line()) + xlab("Method") + ylab("Number of biopsies") + coord_flip() + geom_hline(yintercept = 3, linetype='dashed', color='black')

boxplot_offset_slow =  ggplot() + geom_text(aes(x=1,y=1, label="No cancer progressions.\n Hence no delay."), size=5) + theme(axis.line = element_line(), axis.text = element_blank(), axis.ticks = element_blank(), axis.title = element_blank())

boxplot_slow = ggarrange(boxplot_nb_slow, boxplot_offset_slow, common.legend = T, align = "h", legend = "bottom")

```

## Prostate Cancer Active Surveillance
- To avoid over-treatment, men with low grade prostate cancer are advised active surveillance

<br/>

- <span style="color:red">Cancer progression</span> is tracked via:
    - Prostate-specific antigen measurements
    - Digital rectal exmaination
    - <span style="color:red">Biopsies</span>

<br/>

- Treatment is advised when cancer progression is observed
    - typically via biopsies


## Biopsies vs. Delay in Detection of Cancer Progression
<div style="float: left; width: 50%;">
- <span style="color:black; font-size: 40px">Biopsies</span>
    - are <span style="color:red">burdensome</span> (pain, complications)
    - but <span style="color:green">reliable?</span> sampling errors
</div>

<div style="float: right; width: 50%;">
- <span style="color:black; font-size: 40px">Cancer Progression</span>
    - can only be detected with a certain delay

```{r plot_delay, fig.width=5, fig.height=3, echo = FALSE}
  plot_delay
```
</div>

## Annual Biopsies
- Focus on Minimizing Delay
    - Maximum delay can be 1 year
<br/>
- Many <span style="color:red">unnecessary</span> biopsies for patients who progress slow

```{r plot_annual_delay, fig.width=7, fig.height=3, fig.align="center", echo = FALSE}
  plot_annual_delay
```

## Less Frequent Biopsies - 1

- PRIAS 
    - every 3 years or
    - annually if PSA doubling time < 10 (try to find faster progressions)
    
```{r plot_prias_delay, fig.width=7, fig.height=4, fig.align="center", echo = FALSE}
  plot_prias_delay
```

## Less Frequent Biopsies - 2

- Still <span style="color:red">4 to 10 unnecessary biopsies</span>
    - based on simulation 4-10 unnecessary biopsies for patient with progression >10 years

<br/>

- PRIAS reports <span style="color:red">low compliance (~20%)</span> for Annual biopsy due to PSA-DT.

## A New Approach - 1

<br/>
<br/>

<div style="float: center; text-align: center; width: 700px; border: 3px solid black">
<br/><br/>
<strong><font size="6" color = "red">We need to improve biopsy scheduling</font></strong>
<br/><br/>
</div>

## A New Approach - 2

- Screening based on individualized risk predictions
    - <span style="color:blue">Progression rate is not only different between patients but also dynamically 
changes over time for the same patient</span>

<br/>

- Risk predictions based upon
    - <span style="color:red">All available</span> PSA (ng/mL) measurements
    - <span style="color:red">All available</span> DRE (T1c / above T1c) measurements
    - Time and results of previous biopsies

## A New Approach - 3

```{r, echo = FALSE}
inputPanel(
    fluidPage(
    tags$style(type = 'text/css', 
    ".selectize-input { font-size: 13px; line-height: 13px;} .selectize-dropdown { font-size: 13px;line-height: 13px; }"),
    selectInput("type_plot", label = "Outcome:", 
                 choices = c("survival", "average PSA", "subject PSA")))
)

renderPlot({
    if (input$type_plot == "survival") {
        plot(sfit, mark.time = FALSE, lwd = 1.5, xlab = "Time (years)",
             ylab = "Reclassification-free Probability", main = "Kaplan-Meier Estimate", 
             cex.lab = 1.2, cex.axis = 1.1, col = c(2, 1, 1))
    } else if (input$type_plot == "average PSA") {
        print(xyplot(log2psa ~ visitTimeYears, data = psa_data_set,
                     panel = function (...) {
                         panel.xyplot(..., type = "smooth", col = "red", lwd = 2)
                     },
                     xlab =  "Time (years)", ylab = "log2 PSA", ylim = c(0, 10),
                     par.settings = list(fontsize = list(text = 13, points = 10))))
    } else {
        ids <- c(1336, 50, 2428, 368, 105, 3319, 1005, 344, 3440, 1341, 2921, 2680, 
                 650, 2035, 4071, 461)
        print(xyplot(log2psa ~ visitTimeYears | id,
                     panel = function (x, y, ...) {
                         panel.xyplot(x, y, type = "l", col = 1, ...)
                         if (length(unique(x)) > 5)
                             panel.loess(x, y, col = 2, lwd = 2)
                     }, 
                     data = psa_data_set, subset = id %in% ids, layout = c(4, 4), 
                     as.table = TRUE, xlab = "Time (years)", ylab = "log2 PSA"))
    }
}, width = 800, height = 400)
```

## Joint Models for Risk Predictions - 1

- Challenges in incorporating all available measurements of patients

    - Not all measurements at the same follow-up times for all patients $\rightarrow$ <span style="color:red">Unbalanced dataset</span>
    
    - Patients may miss some visits $\rightarrow$ <span style="color:red">Missing data</span>
    
    - Measurements of PSA and DRE on the same patient more *alike* than measurements from different patients <span style="color:red">Correlations</span>
    
    - Progression affects future values of PSA and DRE $\rightarrow$ <span style="color:red">Endogeneity (standard Cox model not valid)</span>
    
## Joint Models for Risk Predictions - 2

<br/><br/>
<div class="blue">**To account for these challenges we use the framework of**</div>

<br/>

<div style="text-align:center;width:800px;border:3px solid black">
<br/>
<strong><font size="6" color = "red">Joint Models for Longitudinal & Survival Data</font></strong>
<br/>
</div>

## Joint Models for Risk Predictions - 3

```{r, echo = FALSE}
inputPanel(
    sliderInput("measr", label = "Measurements:", min = 1, max = 10, value = 1, step = 1,
                ticks = FALSE,
                animate = animationOptions(interval = 1200, loop = TRUE, 
                                           playButton = NULL, pauseButton = NULL))
)

renderPlot({
    op <- par(mgp = c(2, 0.0, 0), tcl = 0)
    JM::plot.survfitJM(survPrbs[[input$measr]], estimator = "mean", conf.int = TRUE,
                       include.y = TRUE, lwd = 3, ylab = "Risk", fun = function (x) 1 - x,
                       ylab2 = "PSA", xlab = "Time", main = "",
                       cex.axis = 0.001, cex.axis.z = 0.001, cex.lab = 1.2, cex.lab.z = 1.2,
                       col = c(2, 1, 1), fill.area = TRUE, pch = 16, lty = c("11", "99", "99"))
    par(op)
    
}, width = 800, height = 400)
```

## Joint Models for Risk Predictions - 4

- In more detail:

    - We use mixed effects models to describe the longitudinal profiles of each outcome per patient
    
    - We combine these estimated profiles with a time-varying Cox model
    
    - Flexible specification of the association structure
    
## Joint Models for Risk Predictions - 5
```{r, echo = FALSE}
inputPanel(
    sliderInput("measr_3", label = "times:", min = 1, max = 20, value = 1, step = 1,
                ticks = FALSE,
                animate = animationOptions(interval = 1000, loop = FALSE, 
                                           playButton = NULL, pauseButton = NULL))
)

renderPlot({
    set.seed(1234)
    times <- seq(0.01, 10, len = 15)
    m <- rnorm(length(times), 1 + cos(0.5 * times), 0.5)
    h <-  0.5 * 0.8 * times^(0.8-1) * exp(-1.2 * m)
    DD <- data.frame(
        val = c(h, m),
        times = times,
        what = gl(2, length(times), labels = c("hazard function", "longitudinal outcome")))
    i <- input$measr_3
    tts <- seq(0, 10, length = 20)
    print(xyplot(val ~ times | what, data = DD,
                 scales = list(y = list(relation = "free")), layout = c(1, 2), as.table = TRUE,
                 ylab = "", xlab = "Time", panel = function (x, y) {
                     if (panel.number() == 1) {
                         panel.xyplot(x, y, type = "smooth", lwd = 3, col = 2)
                         panel.abline(v = tts[i], lwd = 2, lty = 2,
                                      col = 1)
                     } else {
                         ind <- c(1, 3, 4, 5, 9, 11, 14, 15)
                         panel.xyplot(x[ind], y[ind], type = "p", col = 1, pch = 8,
                                      lwd = 3)
                         panel.abline(v = tts[i], lwd = 2, lty = 2,
                                      col = 1)
                         yy <- 1 + cos(0.5 * x)
                         panel.xyplot(x, yy, type = "l", lwd = 3,
                                      col = 3)
                         #
                         a1 <- tts[i]
                         y1 <- 1 + cos(0.5 * a1)
                         y1d <- - 0.5 * sin(0.5 * a1)
                         xx <- seq(a1 - 0.75, a1 + 0.75, len = 3)
                         extra <- if (a1 < 3) 0.06 else -0.07
                         yy <- y1 + y1d * (xx - a1) + extra
                         panel.xyplot(xx, yy, type = "l", lwd = 3, col = "magenta")
                     }
            }))
}, width = 800, height = 400)
```


## Fitted Joint Model to PRIAS - 1

- describe the model


## Fitted Joint Model to PRIAS - 2
```{r plot_jmFitAssocParam, fig.width=8, fig.height=5, fig.align="center", echo = FALSE}
  plot_jmFitAssocParam
```

## Fitted Joint Model to PRIAS - 3

- Predictions, AUC and prederr



## Personalized Decision Methodology - 1

- Base on the joint model, and at any follow-up time we can calculate a patient's 
 <span style="color:blue">current</span> risk of progression

<br/>

- How to select when to perform a biopsy?

    - **Solution 1:** A fixed treshold, 15% within a year
        - <span style="color:red">however, the same for all time points</span>
        
## Personalized Decision Methodology - 2

- How to select when to perform a biopsy?

    - **Solution 2:** Dynamic treshold based on PRIAS
        - we want both high sensitivity and high positive predictive value
        - we select the treshold that maximizes the F1 score
        $$F1 = 2\frac{SN \times PPV}{SN + PPV}$$

## Personalized Decision Methodology - 3

<br/><br/><br/><br/>

<div align = "center">
<font color = "black" size = "6">**Lets see it in practice...**</font>
</div>




## Comparison: Personalized Vs. Fixed Schedules
- <span style="color:green">Simulation study</span>:
    - Realistic (uses model fitted to the PRIAS dataset).
    - Follow-up time period is 0 to 10 years.
    - 500 datasets x (750 training + 250 test) patients.
    
## Schedules Compared
- <span style="color:red">Fixed</span>:
    - PRIAS (biopsy every 3 years, and if PSA goes up too fast then annual biopsy)
    - Annual (annual biopsies)

- <span style="color:green">Personalized (risk based)</span>:
    - 5% risk threshold
    - 15% risk threshold
    - follow-up time dependent threshold (automatic selection)

### <span style="color:black">Comparison criteria </span>
- Number of biopsies until cancer progression is detected.
- Delay in detection of cancer progression.

## Result: Cancer Progression Times
- <span style="color:black">Slow progression</span>: 50% patients never observe cancer progression in 10 years.
- Remaining 50%:
```{r plot_sim_study_progtime, fig.width=5, fig.height=3, fig.align="center", echo = FALSE}
  plot_sim_study_progtime
```
    - <span style="color:black">Fast progression</span>: 30% patients observe cancer progression in 0 to 3.5 years.
    - <span style="color:black">Intermediate progression</span>: 20% patients observe cancer progression in 3.5 to 10 years.
    
## Result: Performance of Schedules
```{r boxplots}
ui_box <- fluidPage(
  tags$span(style="font-weight: bold; color: black; font-size: 20px;", "Patient Selection: "),
  bsButton("button_boxplot_all", label = "All patients", style = "primary"),
  bsButton("button_boxplot_fast", label = "Fast (30% patients)"),
  bsButton("button_boxplot_intermediate", label = "Intermediate (20% patients)"),
  bsButton("button_boxplot_slow", label = "Slow (50% patients)"),
  hr(),
  plotOutput("plot_boxplot")
)

server_box <- function(input, output, session){
  
  observeEvent(input$button_boxplot_all, {
    updateButton(session, "button_boxplot_all", style="primary")
    updateButton(session, "button_boxplot_fast", style="default")
    updateButton(session, "button_boxplot_intermediate", style="default")
    updateButton(session, "button_boxplot_slow", style="default")
    
    output$plot_boxplot = renderPlot(boxplot_all)
  })
  
  observeEvent(input$button_boxplot_fast, {
    updateButton(session, "button_boxplot_all", style="default")
    updateButton(session, "button_boxplot_fast", style="primary")
    updateButton(session, "button_boxplot_intermediate", style="default")
    updateButton(session, "button_boxplot_slow", style="default")
    
    output$plot_boxplot = renderPlot(boxplot_fast)
  })
  
  observeEvent(input$button_boxplot_intermediate, {
    updateButton(session, "button_boxplot_all", style="default")
    updateButton(session, "button_boxplot_fast", style="default")
    updateButton(session, "button_boxplot_intermediate", style="primary")
    updateButton(session, "button_boxplot_slow", style="default")
    
    output$plot_boxplot = renderPlot(boxplot_intermediate)
  })
  
  observeEvent(input$button_boxplot_slow, {
    updateButton(session, "button_boxplot_all", style="default")
    updateButton(session, "button_boxplot_fast", style="default")
    updateButton(session, "button_boxplot_intermediate", style="default")
    updateButton(session, "button_boxplot_slow", style="primary")
    
    output$plot_boxplot = renderPlot(boxplot_slow)
  })

  output$plot_boxplot <- renderPlot(boxplot_all)
}

shinyApp(ui_box, server_box)
```
