---
title: "Personalized Decisions for Prostate Cancer Biopsies in Active Surveillance"
author: "Anirudh Tomer, Dimitris Rizopoulos"
date: "September 19, 2018"
output:
  ioslides_presentation:
    widescreen: true
    css: main.css
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(ggpubr)
library(shiny)

# FONT_SIZE = 12
# POINT_SIZE = 3
# LARGE_POINT_SIZE = 6
# 
# pat_1757$log2psaplus1 = log(pat_1757$psa + 1, base = 2)
# pat_1757$high_dre = ifelse(pat_1757$dre=="T1c", 0, 1)

load("presetationData.Rdata")

plot_delay =  ggplot() + 
  geom_point(aes(x=c(0, 4, 7), y=0, shape="A", color="A"), size=LARGE_POINT_SIZE) + geom_point(aes(x=5.5, y=0, shape="B", color="B"), size=LARGE_POINT_SIZE) + 
  geom_ribbon(aes(x=c(5.5, 7), ymin=0,ymax=Inf), alpha=0.2) +
  geom_label(aes(x=6.25, y=0.1, label="Delay"), size=5) +
  xlab("Follow-up time (years)") + ylab("") + ylim(0, 0.2) +
  scale_shape_manual("", 
                     labels=c("Biopsies", "Time of cancer progression (unobserved)"),
                     values=c(18,15)) + 
  scale_color_manual("", 
                     labels=c("Biopsies", "Time of cancer progression (unobserved)"),
                     values=c("black", "red3")) + 
  scale_x_continuous(breaks=c(0,4,5.5,7)) + 
  theme(text=element_text(size=FONT_SIZE), axis.line.y = element_blank(), axis.ticks.y = element_blank(), axis.text.y = element_blank(), plot.margin = margin(0,0,0,0),
        legend.position = "bottom", legend.direction = "horizontal", axis.line.x = element_line())

plot_annual_delay =  ggplot() + 
  geom_point(aes(x=c(0:6), y=0, shape="A", color="A"), size=LARGE_POINT_SIZE) + geom_point(aes(x=5.5, y=0, shape="B", color="B"), size=LARGE_POINT_SIZE) + 
  geom_ribbon(aes(x=c(5.5, 6), ymin=0,ymax=Inf), alpha=0.2) +
  geom_label(aes(x=5.75, y=0.1, label="Delay"), size=5) +
  xlab("Follow-up time (years)") + ylab("") + ylim(0, 0.2) +
  scale_shape_manual("", 
                     labels=c("Biopsies", "Time of cancer progression (unobserved)"),
                     values=c(18,15)) + 
  scale_color_manual("", 
                     labels=c("Biopsies", "Time of cancer progression (unobserved)"),
                     values=c("black", "red3")) + 
  scale_x_continuous(breaks=c(0:6, 5.5)) + 
  theme(text=element_text(size=FONT_SIZE), axis.line.y = element_blank(), axis.ticks.y = element_blank(), axis.text.y = element_blank(), plot.margin = margin(0,0,0,0),
        legend.position = "bottom", legend.direction = "horizontal", axis.line.x = element_line())

plot_obs_psa_data = ggplot() + 
    geom_line(data=pat_1757[!is.na(pat_1757$psa),], aes(x=visitTimeYears, y=psa), alpha=0.2, color="dodgerblue4") +
    geom_point(data=pat_1757[!is.na(pat_1757$psa),], aes(x=visitTimeYears, y=psa), shape=16, size=POINT_SIZE, color="dodgerblue4") + 
    geom_vline(data=pat_1757[!is.na(pat_1757$gleason),], aes(xintercept=visitTimeYears, linetype="Biopsies"), size=0.7) +
    scale_linetype_manual("", values="dotted", label="Biopsies") +
  theme(text=element_text(size=FONT_SIZE), plot.margin = margin(0,r = 20,0,0),
        legend.position = "bottom", legend.direction = "horizontal", axis.line.y.left = element_line(), axis.line.x = element_line()) + 
  xlab("Follow-up time (years)") + ylab("PSA (ng/mL)") 

plot_obs_dre_data = ggplot() + 
    geom_line(data=pat_1757[!is.na(pat_1757$high_dre),], aes(x=visitTimeYears, y=high_dre), alpha=0.2, color="darkorchid") +
    geom_point(data=pat_1757[!is.na(pat_1757$high_dre),], aes(x=visitTimeYears, y=high_dre), shape=17, size=POINT_SIZE, color="darkorchid") + 
    geom_vline(data=pat_1757[!is.na(pat_1757$gleason),], aes(xintercept=visitTimeYears, linetype="Biopsies"), size=0.7) +
    scale_linetype_manual("", values="dotted", label="Biopsies") +
  scale_y_continuous(breaks=0:1, labels=c("T1c", "above T1c"), limits = c(0,1)) + 
  theme(text=element_text(size=FONT_SIZE), plot.margin = margin(0,0,0,l=20),
        legend.position = "bottom", legend.direction = "horizontal", axis.line.y.left = element_line(), axis.line.x = element_line()) + 
  xlab("Follow-up time (years)") + ylab("DRE (binary)")
  
plot_obs_data = ggarrange(plot_obs_psa_data, plot_obs_dre_data, nrow=1, ncol=2,
                                  common.legend = T, legend = "bottom")
```

## Prostate Cancer Active Surveillance
- To avoid over-treatment, men with low grade prostate cancer are advised active surveillance.

- Treatment is advised when cancer progression is observed.

- <span style="color:red">Cancer progression</span> is tracked via:
    - Prostate-specific antigen measurements.
    - Digital rectal exmaination. 
    - <span style="color:red">Biopsies.</span>

## Biopsies vs. Delay in Detection of Cancer Progression
<div style="float: left; width: 50%;">
- <span style="color:black; font-size: 40px">Biopsies</span>
    - are <span style="color:red">burdensome</span> (pain, complications).
    - but <span style="color:green">reliable</span> too.
    - are usually conducted with a gap of few months to allow patient to recover.
</div>

<div style="float: right; width: 50%;">
- <span style="color:black; font-size: 40px">Cancer Progression</span>
    - can only be detected with a certain delay.

```{r plot_delay, fig.width=5, fig.height=3, echo = FALSE}
  plot_delay
```
</div>

## Annual Biopsies Focus on Minimizing Delay
- Maximum delay can be 1 year.
- <span style="color:red">Too many biopsies</span> (burdensome) for patients who progress slow.

```{r plot_annual_delay, fig.width=7, fig.height=3, fig.align="center", echo = FALSE}
  plot_annual_delay
```

## PRIAS uses PSA-DT to Identify Faster Progressions

## Can We Personalize Biopsy Decision?
- Decision should depend upon
    - Observed DRE (T1c / above T1c) measurements.
    - Observed PSA (ng/mL) measurements.
    - Time and result of previous biopsies.

```{r plot_obs_data, fig.width=9, fig.height=3, fig.align="center", echo = FALSE}
  plot_obs_data
```

## Joint Model for Time-to-Event and Longitudinal Data
We start talking about joint models from here onwards

## Simulation Study
At some point we talk about simulation study

## Results